Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{{DISTRIBUTION STATEMENT A. Approved for public release.} }

### 2021-05-14 paper/agree.tex
Add Lustre reference

The goal of this section is to illustrate in more detail the process a
system designer follows to add cyber requirements to the AGREE
specifications and then automatically transform the system to insert
the high-assurance components. The AGREE specifications generated by
the transforms for the high-assurance components are then
explained. The section ends with a concise formal statement of the
meaning of an AGREE specification for a high-assurance component. This
meaning is what must be preserved by the synthesis.

@@

The AGREE specification for the SW component in the example of Section~\ref{sec:example} with the added cyber requirements is given in \figref{fig:sw}. The AGREE specification language is a first-order predicate calculus. The semantics are synchronous data-flow where the inputs, outputs, and expressions are characterized by data streams that comply with the input assumptions. The semantics are such that the contracts are evaluated in dependency order with inputs being propagated to outputs through all the contracts until they stabilize; as such, the contracts, and thereby the top-level model, must be acyclic. Once the contracts have stabilized, the model takes a synchronous step to the next input data in the stream. The semantics do not model computation or communication delay. The output of one contract is seen at the input of any downstream contract in the same step of the input data stream.

>>>>

The goal of this section is to illustrate in more detail the process a
system designer follows to add cyber requirements to the AGREE
specifications and then automatically transform the system to insert
the high-assurance components. The AGREE specifications generated by
the transforms for the high-assurance components are
explained. The section ends with a concise formal statement of the
meaning of an AGREE specification for a high-assurance component. This
meaning is what must be preserved by the synthesis.

@@

The AGREE specification for the SW component in the example of Section~\ref{sec:example} with the added cyber requirements is given in \figref{fig:sw}. The AGREE specification language is a first-order predicate calculus that uses stream concepts, and operators, from the Lustre language \cite{10.1145/41625.41641}. As with Lustre, the semantics are synchronous data-flow where the inputs, outputs, and expressions are characterized by data streams that comply with the input assumptions. The semantics are such that the contracts are evaluated in dependency order with inputs being propagated to outputs through all the contracts until they stabilize; as such, the contracts, and thereby the top-level model, must be acyclic. Once the contracts have stabilized, the model takes a synchronous step to the next input data in the stream. The semantics do not model computation or communication delay. The output of one contract is seen at the input of any downstream contract in the same step of the input data stream.
